---
title: "R24-16S"
author: "Katherine Mueller"
date: "10/23/2020"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(phyloseq)
library(readr)
library(readxl)
library(dplyr)
library(ggplot2)
library(cowplot)
library(RColorBrewer)

getPalette = colorRampPalette(brewer.pal(9, "Set1"))
```

## Analysis of Interim Samples
Samples submitted by Brad in 2019

Merge ASV count and taxonomy files
```{r, eval=FALSE}
otu_file <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/second_biom/2020-10-16_update/otu-table.txt"
taxonomy_file <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/second_biom/2020-10-16_update/taxonomy.tsv"

otu_table <- read.table(file = otu_file, header = TRUE)
tax <- read.table(file = taxonomy_file, sep = '\t', header = TRUE)
merged <- merge(otu_table, tax, by.x = c("OTUID"), by.y = c("OTUID"))
write.table(merged, file = "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/second_biom/2020-10-16_update/combined_otu_tax.txt", sep = '\t', col.names = TRUE, row.names = FALSE)
```
The resulting file was then used to create the otu and taxonomy files used in later steps. For ASV, I copied the OTU and count data into a new csv file. For taxonomy, I copied the OTU and taxon data into a new csv file. The taxon data was then split into Kingdom, Phylum, etc. using the text-to-columns option in Excel.

Load in a way to filter for only the samples that are relevant to our isolates
```{r}
#At first, I wanted stool samples with matching Akkermansia isolates
#verruco_percent <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical #Isolates/Data/Data_for_analysis/Community_Analysis/second_biom/2020-10-16_update/verruco_percent.xlsx"

#isolates <- read_excel(verruco_percent)
#samples_with_isolates <- isolates$Isolate

#isolate_subset <- subset_samples(physeq, SampleID %in% samples_with_isolates)

#Now I want stool samples of patients with Akk isolates at any timepoint
human_subjects_details <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/HumanSubjectsAkkermansia_KMupdate.xlsx"
patients_with_isolates <- read_excel(human_subjects_details)
patient_list <- patients_with_isolates$IND
patient_list <- c(patient_list, "Brad")

#I'll want to order graphs by %Verruco
top_verruco_percent <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/second_biom/2020-10-16_update/top_verruco_percent.xlsx"
verruco_list_isolates <- read_excel(top_verruco_percent)
verruco_list <- verruco_list_isolates$Patient
```

Load files into phyloseq
```{r}
otu_matrix_file <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/second_biom/2020-10-16_update/otu-matrix.csv"
taxonomy_matrix_file <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/second_biom/2020-10-16_update/taxonomy-matrix.csv"
map_file <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/second_biom/sample-metadata.txt"

otu_matrix <- read.csv(otu_matrix_file, row.names = 1)
otu_matrix <- as.matrix(otu_matrix)

taxonomy_matrix <- read.csv(taxonomy_matrix_file, row.names = 1)
taxonomy_matrix <- as.matrix(taxonomy_matrix)

metadata <- read_delim(map_file, "\t", escape_double = FALSE, trim_ws = TRUE)
meta_df <- metadata %>% as.data.frame()
meta_df <- meta_df %>% mutate(Patient_f = factor(meta_df$Patient, levels = verruco_list))
row.names(meta_df) <- metadata$SampleID
```

Import as phyloseq objects and merge into one
```{r}
otu <- otu_table(otu_matrix, taxa_are_rows = TRUE)
tax <- tax_table(taxonomy_matrix)
meta <- sample_data(meta_df)

physeq <- phyloseq(otu, tax, meta)
physeq
```

Set up subsets for analysis
```{r}
isolate_subset <- subset_samples(physeq, Patient %in% patient_list)

#Convert abundance counts to percentages. Provided by Jay.
isolate_subset_perc <- transform_sample_counts(isolate_subset, function(x) 100 * x/sum(x))

baseline <- subset_samples(isolate_subset_perc, Visit_number == 1)
endpoint <- subset_samples(isolate_subset_perc, Visit_number == 5)

control <- subset_samples(baseline, Treatment == "control")
base_obese <- subset_samples(baseline, Treatment != "control")
end_obese <- subset_samples(endpoint, Treatment != "control")
```

Count how many samples are in our categories of interest
```{r}
length(sample_names(control))
length(sample_names(base_obese))
length(sample_names(end_obese))
```

Calculate top 20 taxa in samples. Provided by Jay.
```{r}
Calc.Top20 <- function(subset) {
  top_otus <- names(sort(taxa_sums(subset), decreasing = TRUE))[1:20]
  subset_top20 <- prune_taxa(top_otus, subset)
  
  return(subset_top20)
}
```

Plot top 20 OTUs and color by phylum. Provided by Jay.
```{r}
control_top20 <- Calc.Top20(control)
control_plot <- plot_bar(control_top20, x = "Patient", fill = "Phylum") +
  geom_bar(stat = "identity", position = "stack", size = 0) +
  labs(title = "Controls")

base_obese_top20 <- Calc.Top20(base_obese)
base_obese_plot <- plot_bar(base_obese_top20, x = "Patient", fill = "Phylum") +
  geom_bar(stat = "identity", position = "stack", size = 0) +
  labs(title = "Base Obese")

end_obese_top20 <- Calc.Top20(end_obese)
end_obese_plot <- plot_bar(end_obese_top20, x = "Patient", fill = "Phylum") +
  geom_bar(stat = "identity", position = "stack", size = 0) +
  labs(title = "End Obese")

plot_grid(control_plot, base_obese_plot, end_obese_plot, labels = c('A', 'B', 'C'))
```

```{r}
begin_end <- subset_samples(isolate_subset_perc, Visit_number %in% c(1, 5))
begin_end_top20 <- Calc.Top20(begin_end)

begin_end_plot <- barplot <- plot_bar(begin_end_top20, x = "Visit_number", fill = "Phylum") +
  geom_bar(stat = "identity", position = "stack", size = 0) +
  facet_wrap(~ Patient_f) +
  labs(title = "Start and Endpoints by Patient") +
  theme(axis.text.x = element_blank())
begin_end_plot
```

Plot the above, but with just the visit with the most Verrucomicrobia between baseline and endpoint.
```{r}
top_verruco_list <- c("Akk0090", "Akk0196", "Akk0330", "Akk0496", "Akk0500", "Akk0880", "Akk1370", "Akk1410", "Akk1476", "Akk1576", "Akk1610", "Akk1706", "Akk1756", "Akk1810", "Akk1820", "Akk1860", "Akk1900", "Akk1990", "Akk2000", "Akk2030", "Akk2090", "Akk2180", "Akk2190", "Akk2340", "Brad0")
top_verrucos <- subset_samples(begin_end_top20, SampleID %in% top_verruco_list)

top_verrucos_plot1 <- plot_bar(top_verrucos, x = "EMP", fill = "Phylum") +
  geom_bar(stat = "identity", position = "stack", size = 0) +
  facet_wrap(~ Patient_f) +
  theme(axis.text.x = element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank())
top_verrucos_plot1

top_verrucos_plot2 <- plot_bar(top_verrucos, x = "Patient_f", fill = "Phylum") +
  geom_bar(stat = "identity", position = "stack", size = 0) +
  xlab("Patient")
top_verrucos_plot2
```

Plot top 20 OTUs and color by family. Requested for the R24 group.
```{r}
Calc.Top20.fam <- function(subset, graphtitle) {
  top_otus <- names(sort(taxa_sums(subset), decreasing = TRUE))[1:20]
  subset_top20 <- prune_taxa(top_otus, subset)
  barplot <- plot_bar(subset_top20, x = "SampleID", fill = "Family") +
    geom_bar(stat = "identity", position = "stack", size = 0) +
    scale_fill_brewer(palette = "Paired") +
    labs(title = graphtitle)
  
  return(barplot)
}

complete_perc <- transform_sample_counts(physeq, function(x) 100 * x/sum(x))
complete_plot <- Calc.Top20.fam(complete_perc, "Interim Samples")
complete_plot
```

##Analysis of whole dataset
We decided to look at 16S samples beyond those stools that we have isolates for.

```{r}
physeq_perc <- transform_sample_counts(physeq, function(x) 100 * x/sum(x))
baseline_whole <- subset_samples(physeq_perc, Visit_number == 1)
endpoint_whole <- subset_samples(physeq_perc, Visit_number == 5)
```

Baseline visits
```{r}
whole_base_df <- psmelt(baseline_whole)

base_verruco <- whole_base_df %>%
  filter(Phylum == "D_1__Verrucomicrobia") %>%
  group_by(Patient) %>%
  summarise(verruco_abundance = sum(Abundance)) %>%
  as.data.frame()
base_verruco <- base_verruco[order(-base_verruco$verruco_abundance),]
whole_base_df$Patient <- factor(whole_base_df$Patient, levels = base_verruco$Patient)

phyla_palette = c(getPalette(24),"#1B9E77")
whole_base_plot <- ggplot(whole_base_df, aes(x = Patient, y = Abundance, factor(Phylum), fill = factor(Phylum))) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_manual(values = phyla_palette) +
  labs(fill = "Phylum") +
  theme(axis.text.x = element_text(angle = 45))
whole_base_plot
```

Endpoint visits
```{r}
whole_end_df <- psmelt(endpoint_whole)

end_verruco <- whole_end_df %>%
  filter(Phylum == "D_1__Verrucomicrobia") %>%
  group_by(Patient) %>%
  summarise(verruco_abundance = sum(Abundance)) %>%
  as.data.frame()
end_verruco <- end_verruco[order(-end_verruco$verruco_abundance),]
whole_end_df$Patient <- factor(whole_end_df$Patient, levels = end_verruco$Patient)

whole_end_plot <- ggplot(whole_end_df, aes(x = Patient, y = Abundance, factor(Phylum), fill = factor(Phylum))) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_manual(values = phyla_palette) +
  labs(fill = "Phylum") +
  theme(axis.text.x = element_text(angle = 45))
whole_end_plot
```

Alternate baseline and endpoint samples for each patient, organized by %Verruco at baseline
```{r}
#Filter for Patients that have both a baseline and endpoint sample
have_both <- c()
for(i in 1:length(base_verruco$Patient)) {
  if(base_verruco$Patient[i] %in% end_verruco$Patient) {
    have_both <- c(have_both, base_verruco$Patient[i])
  }
}

base_end_whole <- subset_samples(physeq_perc, Visit_number %in% c(1,5))
base_end_whole <- subset_samples(base_end_whole, Patient %in% have_both)
base_end_df <- psmelt(base_end_whole)

#Order by baseline verruco
base_end_verruco <- base_end_df %>%
  filter(Phylum == "D_1__Verrucomicrobia") %>%
  group_by(Patient, Visit_number, SampleID) %>%
  summarize(Verruco_abundance = sum(Abundance))
base_end_verruco$base_verruco <- c()
for(i in 1:length(base_end_verruco$Patient)) {
  base_end_verruco$base_verruco[i] <- base_verruco$verruco_abundance[base_verruco$Patient == base_end_verruco$Patient[i]]
}

base_end_verruco <- base_end_verruco[order(-base_end_verruco$base_verruco),]
base_end_df$SampleID <- factor(base_end_df$SampleID, levels = base_end_verruco$SampleID)

#Graph all together
base_end_plot <- ggplot(base_end_df, aes(x = SampleID, y = Abundance, factor(Phylum), fill = factor(Phylum))) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_manual(values = phyla_palette) +
  labs(fill = "Phylum") +
  theme(axis.text.x = element_text(angle = 45))
base_end_plot

#Graph by Patient
base_end_verruco2 <- base_end_verruco %>% filter(Visit_number == 1)
base_end_df$Patient <- factor(base_end_df$Patient, levels = base_end_verruco2$Patient)
base_end_plot2 <- ggplot(base_end_df, aes(x = Visit_number, y = Abundance, factor(Phylum), fill = factor(Phylum))) +
  facet_wrap(~Patient) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_manual(values = phyla_palette) +
  labs(fill = "Phylum") +
  xlab("Visit") +
  theme(axis.text.x = element_blank())
base_end_plot2
```

We also want a graph for all samples, faceted by PID for obese patients. Healthy controls should be in a plot of their own without faceting.
```{r}
obese_whole <- subset_samples(physeq_perc, Treatment != "control")
obese_df <- psmelt(obese_whole)
healthy_whole <- subset_samples(physeq_perc, Treatment == "control")
healthy_df <- psmelt(healthy_whole)
```

```{r}
obese_plot <- ggplot(obese_df, aes(x = Visit_number, y = Abundance, factor(Phylum), fill = factor(Phylum))) +
  facet_wrap(~Patient) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_manual(values = phyla_palette) +
  labs(fill = "Phylum") +
  xlab("Visit") +
  theme(axis.text.x = element_blank())
obese_plot
```
```{r}
healthy_plot <- ggplot(healthy_df, aes(x = Visit_number, y = Abundance, factor(Phylum), fill = factor(Phylum))) +
  geom_bar(stat = "identity", position = "stack") +
  facet_wrap(~Patient) +
  scale_fill_manual(values = phyla_palette) +
  labs(fill = "Phylum") +
  xlab("Patient ID") +
  theme(axis.text.x = element_blank())
healthy_plot
```


## Analysis of Recent Samples
Samples submitted by Holly in 2020

Merge ASV count and taxonomy files for part 1
```{r, eval=FALSE}
otu_file_1 <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/phyloseq/begin_1_otu_table.txt"
taxonomy_file_1 <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/phyloseq/begin_1_taxonomy.tsv"

otu_table_1 <- read.table(file = otu_file_1, header = TRUE)
tax_1 <- read.table(file = taxonomy_file_1, sep = '\t', header = TRUE)
merged_1 <- merge(otu_table_1, tax_1, by.x = c("OTUID"), by.y = c("OTUID"))
write.table(merged_1, file = "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/phyloseq/begin_1_combined_otu_tax.txt", sep = '\t', col.names = TRUE, row.names = FALSE)
```

Merge ASV count and taxonomy files for part 2
```{r, eval=FALSE}
otu_file_2 <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/phyloseq/begin_2_otu_table.txt"
taxonomy_file_2 <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/phyloseq/begin_2_taxonomy.tsv"

otu_table_2 <- read.table(file = otu_file_2, header = TRUE)
tax_2 <- read.table(file = taxonomy_file_2, sep = '\t', header = TRUE)
merged_2 <- merge(otu_table_2, tax_2, by.x = c("OTUID"), by.y = c("OTUID"))
write.table(merged_2, file = "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/phyloseq/begin_2_combined_otu_tax.txt", sep = '\t', col.names = TRUE, row.names = FALSE)
```

Merge ASV count and taxonomy files for part 3
```{r, eval=FALSE}
otu_file_3 <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/phyloseq/begin_3_otu_table.txt"
taxonomy_file_3 <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/phyloseq/begin_3_taxonomy.tsv"

otu_table_3 <- read.table(file = otu_file_3, header = TRUE)
tax_3 <- read.table(file = taxonomy_file_3, sep = '\t', header = TRUE)
merged_3 <- merge(otu_table_3, tax_3, by.x = c("OTUID"), by.y = c("OTUID"))
write.table(merged_3, file = "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/phyloseq/begin_3_combined_otu_tax.txt", sep = '\t', col.names = TRUE, row.names = FALSE)
```

Load files into phyloseq for part 1
```{r}
otu_matrix_file_1 <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/phyloseq/begin_1_otu-matrix.csv"
taxonomy_matrix_file_1 <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/phyloseq/begin_1_taxonomy-matrix.csv"
map_file_1 <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/2020-07-22_mapping_begin1.txt"

otu_matrix_1 <- read.csv(otu_matrix_file_1, row.names = 1, check.names = FALSE)
otu_matrix_1 <- as.matrix(otu_matrix_1)

taxonomy_matrix_1 <- read.csv(taxonomy_matrix_file_1, row.names = 1)
taxonomy_matrix_1 <- as.matrix(taxonomy_matrix_1)

metadata_1 <- read_delim(map_file_1, "\t", escape_double = FALSE, trim_ws = TRUE)
meta_df_1 <- metadata_1 %>% as.data.frame()
row.names(meta_df_1) <- metadata_1$SampleID
```
Load files into phyloseq for part 2
```{r}
otu_matrix_file_2 <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/phyloseq/begin_2_otu-matrix.csv"
taxonomy_matrix_file_2 <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/phyloseq/begin_2_taxonomy-matrix.csv"
map_file_2 <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/2020-07-22_mapping_begin2.txt"

otu_matrix_2 <- read.csv(otu_matrix_file_2, row.names = 1, check.names = FALSE)
otu_matrix_2 <- as.matrix(otu_matrix_2)

taxonomy_matrix_2 <- read.csv(taxonomy_matrix_file_2, row.names = 1)
taxonomy_matrix_2 <- as.matrix(taxonomy_matrix_2)

metadata_2 <- read_delim(map_file_2, "\t", escape_double = FALSE, trim_ws = TRUE)
meta_df_2 <- metadata_2 %>% as.data.frame()
row.names(meta_df_2) <- metadata_2$SampleID
```

Load files into phyloseq for part 3
```{r}
otu_matrix_file_3 <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/phyloseq/begin_3_otu-matrix.csv"
taxonomy_matrix_file_3 <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/phyloseq/begin_3_taxonomy-matrix.csv"
map_file_3 <- "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/2020-07-22/2020-07-22_mapping_begin3-9.txt"

otu_matrix_3 <- read.csv(otu_matrix_file_3, row.names = 1, check.names = FALSE)
otu_matrix_3 <- as.matrix(otu_matrix_3)

taxonomy_matrix_3 <- read.csv(taxonomy_matrix_file_3, row.names = 1)
taxonomy_matrix_3 <- as.matrix(taxonomy_matrix_3)

metadata_3 <- read_delim(map_file_3, "\t", escape_double = FALSE, trim_ws = TRUE)
meta_df_3 <- metadata_3 %>% as.data.frame()
row.names(meta_df_3) <- metadata_3$SampleID
```
Import as phyloseq objects and merge into one
```{r}
otu_1 <- otu_table(otu_matrix_1, taxa_are_rows = TRUE)
tax_1 <- tax_table(taxonomy_matrix_1)
meta_1 <- sample_data(meta_df_1)

otu_2 <- otu_table(otu_matrix_2, taxa_are_rows = TRUE)
tax_2 <- tax_table(taxonomy_matrix_2)
meta_2 <- sample_data(meta_df_2)

otu_3 <- otu_table(otu_matrix_3, taxa_are_rows = TRUE)
tax_3 <- tax_table(taxonomy_matrix_3)
meta_3 <- sample_data(meta_df_3)

physeq1 <- phyloseq(otu_1, tax_1, meta_1)
glom1 <- tax_glom(physeq1, taxrank = "Species")
physeq2 <- phyloseq(otu_2, tax_2, meta_2)
glom2 <- tax_glom(physeq2, taxrank = "Species")
physeq3 <- phyloseq(otu_3, tax_3, meta_3)
glom3 <- tax_glom(physeq2, taxrank = "Species")

physeq_hiseq <- merge_phyloseq(glom1, glom2, glom3)
physeq_hiseq
```

Plot top 20 OTUs and color by family. Requested for the R24 group.
```{r}
hiseq_perc <- transform_sample_counts(physeq_hiseq, function(x) 100 * x/sum(x))
hiseq_plot <- Calc.Top20.fam(hiseq_perc, "Recent Samples")
hiseq_plot
```

Jay put together a phyloseq containing the results of his analysis. Because this was a larger set of samples than I had, I will use this to try to fill in %Verruco for our supplemental table.

```{r}
phyloseq_subset_AHA <- readRDS("C:/Users/katmu/Downloads/phyloseq_subset_AHA.rds")
phyloseq_subset_AHA
```

```{r}
phyloseq_perc <- transform_sample_counts(phyloseq_subset_AHA, function(x) 100 * x/sum(x))
phyla_only <- tax_glom(phyloseq_perc, "phylum")
phyla_only
```

```{r}
phyla_df <- psmelt(phyla_only)

combined_phyla <- phyla_perc_df %>% group_by(phylum, Sample) %>% summarise(sum_phylum = sum(Abundance))

verrucos_only<- combined_phyla %>% filter(phylum == "Verrucomicrobiota")
```

```{r}
write.csv(verrucos_only, "C:/Users/katmu/Dropbox/Valdivia Lab/Projects/Clinical Isolates/Data/Data_for_analysis/Community_Analysis/Jay_analysis_verrucos.csv", row.names = FALSE)
```

