---
title: "Full Set Analysis"
author: "Katherine Mueller"
date: "3/12/2021"
output: html_document
---

##Setup

#Load Libraries
```{r}
library(readr)
library(phyloseq)
library(tibble)
library(dplyr)
library(ggplot2)
library(microbiomeMarker)
```

#Define Paths
```{r}
r24.rds = "../../Data/Data_for_analysis/Community_Analysis/full_R24/phyloseq_r24_complete_16S_metadata_corrected.rds"
out.dir = "../../Data/Data_for_analysis/Community_Analysis/full_R24"
```

#Load and Check Phyloseq Object
```{r}
r24.ps = read_rds(r24.rds)
print(r24.ps)
```

```{r}
sample_variables(r24.ps)
```
##Processing
#Rename Taxa Titles
```{r}
taxa_table <- tax_table(r24.ps) %>%
  as.data.frame() %>%
  rename(Kingdom = domain, Phylum = phylum, Class = class, Order = order, Family = family, Genus = genus, Species = species) %>%
  as.matrix() %>%
  tax_table()
```

#Recreate phyloseq object
```{r}
asvs <- otu_table(r24.ps)
meta <- sample_data(r24.ps)

r24.ps.goodtaxa <- phyloseq(asvs, meta, taxa_table)
print(r24.ps.goodtaxa)
```

#Filter for Patients and Controls
```{r}
people.ps <- r24.ps.goodtaxa %>%
  subset_samples(group %in% c("HWC", "OB"))
print(people.ps)
```

#Convert ASV Counts to Relative Abundance
```{r}
people.ps.rel <- people.ps %>%
  transform_sample_counts(function(x) x / sum(x))
```

```{r}
head(sample_sums(people.ps.rel))
```

##Make Verruco Abundance into Sample Variables
#Calculate Phylum-level Abundance
```{r}
people.ps.rel.verrucos <- people.ps.rel %>%
  subset_taxa(Phylum == "Verrucomicrobiota") %>%
  tax_glom("Phylum")
print(people.ps.rel.verrucos)
```
```{r}
#First/original column is percent verruco
verrucos <- people.ps.rel.verrucos %>%
  otu_table() %>%
  as.data.frame()
names(verrucos)[1] <- "percent"

#Determine +/- Verruco based on a 0.01% cutoff
verrucos <- verrucos %>%
  mutate(has_verruco = ifelse(percent >= 0.0001, "VerrucoPositive", "VerrucoNegative"))
```

#Assign New Variables
```{r}
sample_data(people.ps.rel)$verruco_abund <- verrucos$percent
sample_data(people.ps.rel)$verruco_presence <- verrucos$has_verruco
```

```{r}
sample_variables(people.ps.rel)
```

##LEfSe Analysis
```{r}
ps.family <- people.ps.rel %>%
  tax_glom(taxrank = "Family")

lef <- lefse(ps.family,
             class = "verruco_presence",
             multicls_strat = TRUE)
```

```{r}
plot_ef_bar(lef)
```

##Investigation of Akkermansia ASVs
I want to determine the sequences of Akkermansia ASVs in order to align them with the V3-V4 sequences of our isolates and determine which phylogroups these ASVs are likely to belong to.
#Pull Akkermansia ASVs
Filter through all the taxa to pull out just those that are labeled as Akkermansia, then prune for just those ASVs that appear at an average abundance of 0.01% in the entire data set.
```{r}
mean_cutoff = 0.001
mean_test = function(x) {
  mean(x) >= mean_cutoff
}

people.ps.rel.akks <- people.ps.rel %>%
  subset_taxa(Genus == "Akkermansia") %>%
  filter_taxa(mean_test, prune = TRUE)
print(people.ps.rel.akks)
```
This resulted in two Akkermansia ASVs, so now I want the sequences.
```{r}
akks <- people.ps.rel.akks %>%
  otu_table() %>%
  as.data.frame()
colnames(akks)[1]
colnames(akks)[2]
```
