---
title: "Full Set Analysis"
author: "Katherine Mueller"
date: "3/12/2021"
output: html_document
---

##Setup

#Load Libraries
```{r}
library(readr)
library(phyloseq)
library(tibble)
library(dplyr)
library(ggplot2)
library(microbiomeMarker)
library(tidyr)
```

#Define Paths
```{r}
r24.rds = "../../Data/Data_for_analysis/Community_Analysis/full_R24/phyloseq_r24_complete_16S_metadata_corrected.rds"
out.dir = "../../Data/Data_for_analysis/Community_Analysis/full_R24"
```

#Load and Check Phyloseq Object
```{r}
r24.ps = read_rds(r24.rds)
print(r24.ps)
```

```{r}
sample_variables(r24.ps)
```

##Functions
Count the number of times a phylogroup or combination of phylogroups is counted in samples. Takes a phyloseq object and a string. The string needs to be "noAm24" if you don't think that the combination of AmII and AmIV will occur in any samples in order to avoid non-zero dimension errors.
```{r}
phylogroup_counts <- function(ps, am24) {
  #Since the AmII/AmIv combo is the only one that is super rare, every other combo can be counted without error
  counts <- c(
    no_akk = nsamples(subset_samples(ps, AmI_presence == "AmI_Negative" & AmII_presence == "AmII_Negative" & AmIV_presence == "AmIV_Negative")),
    AmI = nsamples(subset_samples(ps, AmI_presence == "AmI_Positive")),
    AmII = nsamples(subset_samples(ps, AmII_presence == "AmII_Positive")),
    AmIV = nsamples(subset_samples(ps, AmIV_presence == "AmIV_Positive")),
    AmI_AmII = nsamples(subset_samples(ps, AmI_presence == "AmI_Positive" & AmII_presence == "AmII_Positive")),
    AMI_AmIV = nsamples(subset_samples(ps, AmI_presence == "AmI_Positive" & AmIV_presence == "AmIV_Positive")))
  
  #The last step depends on the presence/absence of the AmII/AmIV combo
  ifelse(am24 == "noAm24",
         #If no Am2/Am4 combo, count is zero
         counts <- c(counts, AmII_AmIV = 0),
         #Else, count like usual
         counts <- c(counts,
                     AmII_AmIV = nsamples(subset_samples(ps, AmII_presence == "AmII_Positive" & AmIV_presence == "AmIV_Positive")))
  )
  
  return(counts)
}
```

##Processing
#Rename Taxa Titles
```{r}
taxa_table <- tax_table(r24.ps) %>%
  as.data.frame() %>%
  rename(Kingdom = domain, Phylum = phylum, Class = class, Order = order, Family = family, Genus = genus, Species = species) %>%
  as.matrix() %>%
  tax_table()
```

#Recreate phyloseq object
```{r}
asvs <- otu_table(r24.ps)
meta <- sample_data(r24.ps)

r24.ps.goodtaxa <- phyloseq(asvs, meta, taxa_table)
print(r24.ps.goodtaxa)
```

#Filter for Patients and Controls
```{r}
people.ps <- r24.ps.goodtaxa %>%
  subset_samples(group %in% c("HWC", "OB"))
print(people.ps)
```

#Convert ASV Counts to Relative Abundance
```{r}
people.ps.rel <- people.ps %>%
  transform_sample_counts(function(x) x / sum(x))
```

```{r}
head(sample_sums(people.ps.rel))
```

##Make Verruco Abundance into Sample Variables
#Calculate Phylum-level Abundance
```{r}
people.ps.rel.verrucos <- people.ps.rel %>%
  subset_taxa(Phylum == "Verrucomicrobiota") %>%
  tax_glom("Phylum")
print(people.ps.rel.verrucos)
```
```{r}
#First/original column is percent verruco
verrucos <- people.ps.rel.verrucos %>%
  otu_table() %>%
  as.data.frame()
names(verrucos)[1] <- "percent"

#Determine +/- Verruco based on a 0.01% cutoff
verrucos <- verrucos %>%
  mutate(has_verruco = ifelse(percent >= 0.0001, "VerrucoPositive", "VerrucoNegative"))
```

#Assign New Variables
```{r}
sample_data(people.ps.rel)$verruco_abund <- verrucos$percent
sample_data(people.ps.rel)$verruco_presence <- verrucos$has_verruco
```

```{r}
sample_variables(people.ps.rel)
```

How many samples have Verrucos?
```{r}
nsamples(people.ps.rel)
nsamples(subset_samples(people.ps.rel, verruco_presence == "VerrucoPositive"))
```
701/790 samples have an abundance of at least 0.01% Verruco. 

##Investigation of Akkermansia ASVs
I want to determine the sequences of Akkermansia ASVs in order to align them with the V3-V4 sequences of our isolates and determine which phylogroups these ASVs are likely to belong to.

Before any filtering, I should determine how many Akkermansia ASVs have been identified in total.
```{r}
akks.ps.rel <- people.ps.rel %>%
  subset_taxa(Genus == "Akkermansia")
print(akks.ps.rel)
```

#First-pass Filtering
Filter through all the taxa to pull out just those that are labeled as Akkermansia, then prune for just those ASVs that appear at an average abundance of 0.01% or higher in the entire data set.
```{r}
mean_cutoff = 0.0001
mean_test = function(x) {
  mean(x) >= mean_cutoff
}

akks.ps.rel.0001mean <- akks.ps.rel %>%
  filter_taxa(mean_test, prune = TRUE)
print(akks.ps.rel.0001mean)
```

This resulted in three Akkermansia ASVs, so now I want the sequences.
```{r}
akks <- akks.ps.rel.0001mean %>%
  otu_table() %>%
  as.data.frame()
colnames(akks)
```

#Less stringent filtering
I want to see how many Akkermansia ASVs there are that appear at an abundance of 0.1% or 0.01% in at least one sample.
```{r}
min_fraction = 0.001
min_samples = 1
akks.ps.rel.001anysample <- akks.ps.rel %>%
  filter_taxa(function(x) sum(x >= min_fraction) >= min_samples,
              prune = TRUE)
print(akks.ps.rel.001anysample)
```

```{r}
akks <- akks.ps.rel.001anysample %>%
  otu_table() %>%
  as.data.frame()
colnames(akks)
```

```{r}
min_fraction = 0.0001
min_samples = 1
akks.ps.rel.0001anysample <- akks.ps.rel %>%
  filter_taxa(function(x) sum(x >= min_fraction) >= min_samples,
              prune = TRUE)
print(akks.ps.rel.0001anysample)
```

```{r}
akks <- akks.ps.rel.0001anysample %>%
  otu_table() %>%
  as.data.frame()
colnames(akks)
```

I want to make a box plots of the abundances of these ASVs to see if I really need all 15, or can go with one of the more stringent filters.
```{r}
#rename sequences to be human-distinguishable
colnames(akks)[1] <- "mean.1"
colnames(akks)[2] <- "mean.2"
colnames(akks)[3] <- "mean.3"
colnames(akks)[4] <- "any1.4"
colnames(akks)[5] <- "any01.5"
colnames(akks)[6] <- "any01.6"
colnames(akks)[7] <- "any01.7"
colnames(akks)[8] <- "any01.8"
colnames(akks)[9] <- "any01.9"
colnames(akks)[10] <- "any01.10"
colnames(akks)[11] <- "any01.11"
colnames(akks)[12] <- "any01.12"
colnames(akks)[13] <- "any01.13"
colnames(akks)[14] <- "any01.14"
colnames(akks)[15] <- "any01.15"
```

```{r}
#make akks dataframe tidy
akks.long <- akks %>%
  gather(ASV, Abundance, "mean.1":"any01.15")

#plot boxes
akks.boxplot <- akks.long %>%
  ggplot(aes(x = ASV, y = Abundance)) +
  geom_point() +
  geom_jitter()
akks.boxplot
```

Based on an outside comparison of the ASV sequences and the V3-V4 sequences of our isolates, as well as the near-zero abundance of all but the top three ASVs, I will concentrate on just those three.
From the outside comparison, I had determined that the mean-1 SV is most likely an AmI, the mean-2 SV is an AmIV, and the mean-3 SV is an AmII.

How many samples have Akkermansia when we're only looking at those top three ASVs?
```{r}
#Determine presence/absence of each phylogroup
akks <- akks %>%
  select(mean.1, mean.2, mean.3) %>%
  mutate(Akk_abundance = rowSums(.),
         has_AmI = ifelse(mean.1 >= 0.0001, "AmI_Positive", "AmI_Negative"),
         has_AmII = ifelse(mean.3 >= 0.0001, "AmII_Positive", "AmII_Negative"),
         has_AmIV = ifelse(mean.2 >= 0.0001, "AmIV_Positive", "AmIV_Negative"),
         has_Akk = ifelse(Akk_abundance >= 0.0001, "Akk_Positive", "Akk_Negative"))

#Assign new variables
sample_data(people.ps.rel)$AmI_abund <- akks$mean.1
sample_data(people.ps.rel)$AmI_presence <- akks$has_AmI
sample_data(people.ps.rel)$AmII_abund <- akks$mean.3
sample_data(people.ps.rel)$AmII_presence <- akks$has_AmII
sample_data(people.ps.rel)$AmIV_abund <- akks$mean.2
sample_data(people.ps.rel)$AmIV_presence <- akks$has_AmIV
sample_data(people.ps.rel)$Akk_abund <- akks$Akk_abundance
sample_data(people.ps.rel)$Akk_presence <- akks$has_Akk
```

```{r}
sample_variables(people.ps.rel)
```

```{r}
akk_stats <- data.frame(total_samples = nsamples(people.ps.rel),
                       total_akk = nsamples(subset_samples(people.ps.rel, AmI_presence == "AmI_Positive" | AmII_presence == "AmII_Positive" | AmIV_presence == "AmIV_Positive")),
                       AmI = nsamples(subset_samples(people.ps.rel, AmI_presence == "AmI_Positive")),
                       AmII = nsamples(subset_samples(people.ps.rel, AmII_presence == "AmII_Positive")),
                       AmIV = nsamples(subset_samples(people.ps.rel, AmIV_presence == "AmIV_Positive")),
                       AmI_AmII = nsamples(subset_samples(people.ps.rel, AmI_presence == "AmI_Positive" & AmII_presence == "AmII_Positive")),
                       AmI_AmIV = nsamples(subset_samples(people.ps.rel, AmI_presence == "AmI_Positive" & AmIV_presence == "AmIV_Positive")),
                       AmII_AmIV = nsamples(subset_samples(people.ps.rel, AmII_presence == "AmII_Positive" & AmIV_presence == "AmIV_Positive"))
                       #This last one creates an error for not having anything that passes the filter
                       #all_Am = nsamples(subset_samples(people.ps.rel, AmI_presence == "AmI_Positive" & AmII_presence == "AmII_Positive" & AmIV_presence == "AmIV_Positive"))
                       )
akk_stats
```
588/790 samples have an abundance of at least 0.01% of at least one of the top three Akkermansia ASVs. 532 have an abundance of at least 0.01% AmI, 65 have an abundance of at least 0.01% Am2, and 87 have an abundance of at least 0.01% AmIV.
44 samples contain both AmI and AmII at an abundance of at least 0.01% each. 51 samples contain both AmI and AmIV at at least 0.01% abundance each, and 1 sample contains both AmII and AmIV at at least 0.01% abundance each. There are no samples that contain all three phylogroups

Does the percentage of samples with each phylogroup differ between the obese and healthy control groups?
```{r}
obese.ps.rel <- people.ps.rel %>%
  subset_samples(group == "OB")
healthy.ps.rel <- people.ps.rel %>%
  subset_samples(group == "HWC")

obese_stats <- phylogroup_counts(obese.ps.rel, "noAm24")
healthy_stats <- phylogroup_counts(healthy.ps.rel, "yesAm24")

data.frame(obese_stats, healthy_stats)
```


##LEfSe Analysis
```{r}
ps.family <- people.ps.rel %>%
  tax_glom(taxrank = "Family")

lef <- lefse(ps.family,
             class = "Akk_presence",
             multicls_strat = TRUE)
```

```{r}
plot_ef_bar(lef)
```

Are there taxa associated with individual phylogroups?
```{r}
haveakk.ps.rel <- people.ps.rel %>%
  subset_samples(Akk_presence == "Akk_Positive")

lef.AmI <- lefse(haveakk.ps.rel,
                 class = "AmI_presence",
                 multicls_strat = TRUE)
lef.AmII <- lefse(haveakk.ps.rel,
                 class = "AmII_presence",
                 multicls_strat = TRUE)
lef.AmIV <- lefse(haveakk.ps.rel,
                 class = "AmIV_presence",
                 multicls_strat = TRUE)
```

```{r}
plot_ef_bar(lef.AmI)
```

```{r}
plot_ef_bar(lef.AmII)
```

```{r}
plot_ef_bar(lef.AmIV)
```

