---
title: "Full Set Analysis"
author: "Katherine Mueller"
date: "3/12/2021"
output: html_document
---

##Setup

#Load Libraries
```{r}
library(readr)
library(phyloseq)
library(tibble)
library(dplyr)
library(ggplot2)
library(microbiomeMarker)
```

#Define Paths
```{r}
r24.rds = "../../Data/Data_for_analysis/Community_Analysis/full_R24/phyloseq_r24_complete_16S_metadata_corrected.rds"
out.dir = "../../Data/Data_for_analysis/Community_Analysis/full_R24"
```

#Load and Check Phyloseq Object
```{r}
r24.ps = read_rds(r24.rds)
print(r24.ps)
```

```{r}
sample_variables(r24.ps)
```
##Processing
#Rename Taxa Titles
```{r}
taxa_table <- tax_table(r24.ps) %>%
  as.data.frame() %>%
  rename(Kingdom = domain, Phylum = phylum, Class = class, Order = order, Family = family, Genus = genus, Species = species) %>%
  as.matrix() %>%
  tax_table()
```

#Recreate phyloseq object
```{r}
asvs <- otu_table(r24.ps)
meta <- sample_data(r24.ps)

r24.ps.goodtaxa <- phyloseq(asvs, meta, taxa_table)
print(r24.ps.goodtaxa)
```

#Filter for Patients and Controls
```{r}
people.ps <- r24.ps.goodtaxa %>%
  subset_samples(group %in% c("HWC", "OB"))
print(people.ps)
```

#Convert ASV Counts to Relative Abundance
```{r}
people.ps.rel <- people.ps %>%
  transform_sample_counts(function(x) x / sum(x))
```

```{r}
head(sample_sums(people.ps.rel))
```

##Make Verruco Abundance into Sample Variables
#Calculate Phylum-level Abundance
```{r}
people.ps.rel.verrucos <- people.ps.rel %>%
  subset_taxa(Phylum == "Verrucomicrobiota") %>%
  tax_glom("Phylum")
print(people.ps.rel.verrucos)
```
```{r}
#First/original column is percent verruco
verrucos <- people.ps.rel.verrucos %>%
  otu_table() %>%
  as.data.frame()
names(verrucos)[1] <- "percent"

#Determine +/- Verruco based on a 0.01% cutoff
verrucos <- verrucos %>%
  mutate(has_verruco = ifelse(percent >= 0.0001, "VerrucoPositive", "VerrucoNegative"))
```

#Assign New Variables
```{r}
sample_data(people.ps.rel)$verruco_abund <- verrucos$percent
sample_data(people.ps.rel)$verruco_presence <- verrucos$has_verruco
```

```{r}
sample_variables(people.ps.rel)
```

##LEfSe Analysis
```{r}
ps.family <- people.ps.rel %>%
  tax_glom(taxrank = "Family")

lef <- lefse(ps.family,
             class = "verruco_presence",
             multicls_strat = TRUE)
```

```{r}
plot_ef_bar(lef)
```

##Investigation of Akkermansia ASVs
I want to determine the sequences of Akkermansia ASVs in order to align them with the V3-V4 sequences of our isolates and determine which phylogroups these ASVs are likely to belong to.

Before any filtering, I should determine how many Akkermansia ASVs have been identified in total.
```{r}
akks.ps.rel <- people.ps.rel %>%
  subset_taxa(Genus == "Akkermansia")
print(akks.ps.rel)
```

#First-pass Filtering
Filter through all the taxa to pull out just those that are labeled as Akkermansia, then prune for just those ASVs that appear at an average abundance of 0.01% or higher in the entire data set.
```{r}
mean_cutoff = 0.0001
mean_test = function(x) {
  mean(x) >= mean_cutoff
}

akks.ps.rel.0001mean <- akks.ps.rel %>%
  filter_taxa(mean_test, prune = TRUE)
print(akks.ps.rel.0001mean)
```

This resulted in two Akkermansia ASVs, so now I want the sequences.
```{r}
akks <- akks.ps.rel.0001mean %>%
  otu_table() %>%
  as.data.frame()
colnames(akks)
```

#Less stringnent filtering
I want to see how many Akkermansia ASVs there are that appear at an abundance of 0.1% or 0.01% in at least one sample.
```{r}
min_fraction = 0.001
min_samples = 1
akks.ps.rel.001anysample <- akks.ps.rel %>%
  filter_taxa(function(x) sum(x >= min_fraction) >= min_samples,
              prune = TRUE)
print(akks.ps.rel.001anysample)
```
```{r}
akks <- akks.ps.rel.001anysample %>%
  otu_table() %>%
  as.data.frame()
colnames(akks)
```

```{r}
min_fraction = 0.0001
min_samples = 1
akks.ps.rel.0001anysample <- akks.ps.rel %>%
  filter_taxa(function(x) sum(x >= min_fraction) >= min_samples,
              prune = TRUE)
print(akks.ps.rel.0001anysample)
```
```{r}
akks <- akks.ps.rel.0001anysample %>%
  otu_table() %>%
  as.data.frame()
colnames(akks)
```
