---
title: "LEfSe_analysis"
author: "Katherine Mueller"
date: "4/26/2021"
output: html_document
---

##LEfSe analysis for R24 sample series
Generation of significant and effect size evaluations. It's better to just then take the output into GraphPad Prism to make good-looking graphs.

##Setup
#Load Libraries
```{r}
library(dplyr)
library(readr)
library(phyloseq)
library(tibble)
library(ggplot2)
library(microbiomeMarker)
```

#Define Paths
```{r}
phylogroups.rds = "../../Data/Data_for_analysis/Community_Analysis/full_R24/r24_phylogroups.rds"
out.dir = "../../Data/Data_for_analysis/Community_Analysis/full_R24"
```

#Load and Check Phyloseq Object
```{r}
phylogroups.ps = read_rds(phylogroups.rds)
print(phylogroups.ps)
```

```{r}
sample_variables(phylogroups.ps)
```

##LEfSe Analysis
#Initial Tries
```{r}
family.ps <- phylogroups.ps %>%
  tax_glom(taxrank = "Family")

lef <- lefse(family.ps,
             class = "Akk_presence",
             multicls_strat = TRUE)
```

```{r}
plot_ef_bar(lef)
```

Are there taxa associated with individual phylogroups?
```{r}
haveakk.ps <- phylogroups.ps %>%
  subset_samples(Akk_presence == "Akk_Positive")

lef.AmI <- lefse(haveakk.ps,
                 class = "AmI_presence",
                 multicls_strat = TRUE)
lef.AmII <- lefse(haveakk.ps,
                 class = "AmII_presence",
                 multicls_strat = TRUE)
lef.AmIV <- lefse(haveakk.ps,
                 class = "AmIV_presence",
                 multicls_strat = TRUE)
```

```{r}
plot_ef_bar(lef.AmI)
```

```{r}
plot_ef_bar(lef.AmII)
```

```{r}
plot_ef_bar(lef.AmIV)
```

#Cleaner Method

Filter for ASVs which were identifiable down to the genus level
```{r}
goodgenus.ps <- phylogroups.ps %>%
  subset_taxa(!is.na(Genus))
print(goodgenus.ps)
```

Simplify LEfSe output
```{r}
#Combine the genus and species identifications
taxa <- tax_table(goodgenus.ps) %>%
  as.data.frame()
taxa$Genus_new <- paste(taxa$Genus, taxa$Species, sep = "_")

#Get rid of everything but the genus/species combo name
new.taxa <- taxa %>%
  select(Genus_new)
colnames(new.taxa)[1] <- "Genus"

#Replace the taxa table in the phyloseq object with the new genus/species only table
clean.phylogroups.ps <- goodgenus.ps
tax_table(clean.phylogroups.ps) <- as.matrix(new.taxa)
```

We'll just look at thoses samples that had some level of Akkermansia for phylogroup-pyhylogroup comparisons
```{r}
clean.hasakks.ps <- clean.phylogroups.ps %>%
  subset_samples(Akk_presence == "Akk_Positive")
print(clean.hasakks.ps)
```

Perform LefSe Analyses for phylogroup-phylogroup comparisons
```{r}
#AmI
amI.lef <- lefse(clean.hasakks.ps,
                 class = "AmI_presence",
                 correct = "1")

#AmII
amII.lef <- lefse(clean.hasakks.ps,
                 class = "AmII_presence",
                 correct = "1")

#AmIV
amIV.lef <- lefse(clean.hasakks.ps,
                 class = "AmIV_presence",
                 correct = "1")
```

Check plots
```{r}
plot_ef_bar(amI.lef)
plot_ef_bar(amII.lef)
plot_ef_bar(amIV.lef)
```

```{r}
marker_table(lef.AmI) -> amI.table
marker_table(lef.AmII) -> amII.table
marker_table(lef.AmIV) -> amIV.table

write.csv(amI.table, file.path(out.dir, "amI_lefse.csv"))
write.csv(amII.table, file.path(out.dir, "amII_lefse.csv"))
write.csv(amIV.table, file.path(out.dir, "amIV_lefse.csv"))
```
